\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Clemson Build Constitution \\
\large Version 2}
\date{Updated Jun 8, 2024}

\begin{document}

\maketitle

\section{Introduction}
Clemson Build shall be a registered Independent Student Organization at Clemson University that serves as an incubator for innovative ideas, providing a dynamic environment that fosters collaborative development and realization of projects. By encouraging the exchange of skills, ideas, and skill sharing, we nurture creativity and entrepreneurship.

Our primary role is to be a conduit for success, empowering project founders and contributors by providing them access to necessary resources, including funding, networking opportunities, and other pertinent tools. The ambitious aim is to provide a launchpad for these projects to evolve into full-fledged startups, with the potential to attract investors.

Clemson Build exists to provide a platform for ideas to take flight; we are a community of dreamers, doers, and innovators. Let's build the future, together.
\subsection{Objectives}
Clemson Build's primary objectives shall be as follows:

\begin{itemize}
    \item{Raise funds for the continued growth of the club}
    \item{Support founders and builders with project funding}
    \item{Provide networking opportunities to students}
    \item{Foster a rich environment of diverse ideation among students}
\end{itemize}

\newpage

\section{Structure}

\subsection{Executive Operations}
Executives shall be entrusted with the comprehensive management of club operations, which includes:

\begin{itemize}
\item Conducting meetings
\item Networking with potential and current donors
\item Organizing fundraising events
\item Liaising with Clemson University
\end{itemize}

\subsubsection{Roles}
The Executive Board shall consist of the following roles and their initial holders as of the club's inception:

\begin{itemize}
    \item \textbf{President}: Hunter Sutcliffe
    \item \textbf{Vice President}: Nathan Goller-Deitsch
    \item \textbf{Treasurer}: John O'Neill
    \item \textbf{Secretary}: Regan O'Neill
    \item \textbf{Social Media Coordinator}: Megan DeGrezia
\end{itemize}

All members of the Executive Board during the club's first operational year shall be known as \textbf{Founders} or \textbf{Founding Members}. The \textbf{President} and \textbf{Vice President} shall each hold 49\% of the club's bank account, while the \textbf{Treasurer} shall hold 2\% (collectively, \textbf{Holding Members}). This holding shall be in the interest of the club; Holding Members possess no personal ownership or interest in the club's funds, and may only act as agents of Clemson Build.

\subsubsection{Elections}

Elections will be held at least once per school year, though they may be held more frequently if necessary. The conditions to run for an executive position are as follows:

\begin{itemize}
    \item Must be a current undergraduate Clemson University student
    \item Must be in good standing with the university
    \item Must have attended at least two meetings in the semester of the election (or, if the election is held during a break, the semester immediately prior to the election) \textbf{or} have been a prior member of the Executive Board
\end{itemize}

The conditions to vote in an election are as follows:

\begin{itemize}
    \item Must be a current undergraduate Clemson University student
    \item Must be in good standing with the university
    \item Must have attended at least one meeting in the semester of the election (or, if the election is held during a break, the semester immediately prior to the election) \textbf{or} have been a prior member of the Executive Board
    \item Must intend to attend at least one meeting in the semester following the election
\end{itemize}

Elections will involve a nomination process in which any member may nominate themselves or another member for a position. If a member is nominated by another member, they must accept the nomination to be considered. If a member nominates themselves, they are automatically considered. After nominations are closed, members will perform a fair and anonymous vote to determine the winner of each position.

\subsection{Projects}
The primary focus of the group shall be supporting student-led projects such as startups, open-source software, and portfolio work. 

\subsection{Meetings}
The club shall regularly host meetings including guest speakers, project check-ins, and social events. Meetings shall typically last for one hour and be held once a week. They shall include a dedicated presentation to introduce new projects, update existing projects, and facilitate discussions. After this presentation, members shall be free to network, work on projects, or learn from their peers. Special events may not follow the same structure. 

\subsection{Amendments}
Amendments to this constitution may be made at any time in the event of a majority agreement (50\% or more) of Executive Board members. All constitutional amendments should be made through GitHub on the official \LaTeX{ }document.

\subsection{Additional Provisions}

\begin{itemize}
    \item In the interest of transparency, the club shall disclose to all current members the amount, date, and recipient of each project funding transaction made using club funds within no more than 30 days. Executives are encouraged, but not required, to additionally disclose non-project-related transactions and to make disclosures to the Clemson community at large.
    \item All transactions made with funds acquired from Clemson University's Student Funding Board shall follow relevant guidelines. 
    \item Each project that incorporates shall be required to function under its own liability shield (such as an LLC), separate from the organization's entity.
\end{itemize}
\end{document}
